A Technique for Inter-Catalogue Recommendations

### 2014-06-11 paper2/paper.tex
Edits to Evaluation section

\section*{Evaluation}
Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms \cite{Powers2011}. Together, these metrics capture how
effective one is at guessing items within a target set. Consider a typical
Macy's category, for example, Dresses, which contains approximately $3,500$
items. Suppose that randomly partitioning results in two sets, each with about
$1,750$ items. For each interset recommendation, we must therefore choose two
nodes, one from each of the two sets. That is, we have $1,750 \times 1,750 > 3
\times 10^6$ choices. Choosing the correct edges is a formidable challenge to
say the least. It is therefore worth asking: Are some prediction errors better
or worse than others?

@@

The following definitions will prove helpful. Let $G$ be the original
unpartitioned graph formed from the partitions together with the lost edges $L$
and let $G^{\prime}$ be the new graph formed from the partitions together with
the predicted edges $P$.  In the context of {\em 2-precision}, an edge in $P$
that connects items $A$ and $B$ is considered correct if 1) $A$ and $B$ share an
edge within $G$ or 2) $A$ shares an edge with a direct neighbor of $B$ within
$G$ or 3) a direct neighbor of $A$ shares an edge with $B$ within $G$.
Meanwhile, in the context of {\em 2-recall}, an edge in $L$ that connects items
$C$ and $D$ is considered recalled if 1) $C$ and $D$ share an edge within
$G^{\prime}$ or 2) $C$ shares an edge with a direct neighbor of $D$ within
$G^{\prime}$ or 3) a direct neighbor of $C$ shares an edge with $D$ within
$G^{\prime}$.

We use both traditional precision, recall, and $F_1$ score as well as {\em
2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ score to evaluate our prediction
algorithms. Including the latter set of metrics provides a more complete picture
of algorithmic performance. These additional metrics also accommodate the fact
that the edges of $G$ do not necessarily correspond to the only or even the best
item-item recommendations. We therefore suggest that while traditional precision
and recall are relevant metrics, relative performance as measured by {\em
2-precision} and {\em 2-recall} better captures the effectiveness of these
prediction algorithms.

>>>>

\section*{Evaluation}
Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms \cite{Powers2011}. Together, these metrics capture how
effective one is at guessing items within a target set. Consider a typical
Macy's category, for example, Dresses, which contains approximately $3,500$
items. Suppose that a random partition results in two sets with approximately
$1,750$ items in each. Such a partition would cut approximately half of all the
edges in the unpartioned graph. Since each node has on average eight edges
before partitioning (four in and four out in the original directed graph) and
each edge is shared by two nodes, there are originally a total of approximately
$\left(8 \times 3,500\right) / 2 = 14,000$ edges. This implies that there are
$7,000$ withheld edges in the cut. For each predicted recommendation, we must
choose two nodes, one from each of the two sets. Therefore we have $\left(1,750 \times
1,750\right)/2 > 1 \times 10^6$ choices and only $7,000$ of them are correct. Choosing the
correct edges is a formidable challenge to say the least. It is therefore worth
asking: Are some prediction errors better or worse than others?

@@

The following definitions will prove helpful. Let $G$ be the original
unpartitioned graph, formed from the partitions together with the lost edges
$L$, and let $G^{\prime}$ be the new graph, formed from the partitions together
with the predicted edges $P$.  In the context of {\em 2-precision}, an edge in
$P$ that connects items $A$ and $B$ is considered correct if 1) $A$ and $B$
share an edge in $G$ or 2) $A$ shares an edge with a direct neighbor of $B$ in
$G$ or 3) a direct neighbor of $A$ shares an edge with $B$ within $G$.
Meanwhile, in the context of {\em 2-recall}, an edge in $L$ that connects items
$C$ and $D$ is considered recalled if 1) $C$ and $D$ share an edge in
$G^{\prime}$ or 2) $C$ shares an edge with a direct neighbor of $D$ in
$G^{\prime}$ or 3) a direct neighbor of $C$ shares an edge with $D$ in
$G^{\prime}$.

We use traditional precision, recall, and $F_1$ score as well as {\em
2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ score to evaluate our prediction
algorithms. Including the latter set of metrics provides a more complete picture
of algorithmic performance. These additional metrics also accommodate the fact
that the edges of $G$ do not necessarily correspond to the only or even the best
item-item recommendations. We therefore suggest that while traditional precision
and recall are relevant metrics, relative performance as measured by {\em
2-precision} and {\em 2-recall} better captures the effectiveness of these
prediction algorithms.
